\chapter{Acknowledgements}
\thispagestyle{empty}
\comment{ funding bodies
    supervisors
    professor
    laboratory assistants
    librarians
    colleagues
    editors/proofreaders (a requirement at some universities)
    classmate
    research participants (e.g. people who completed a survey to help you gather data)}

\noindent%
Completing my master's thesis during an ongoing pandemic was a big challenge; both personally and professionally. It was through the constant support of my supervisors, family and friends that I have been able to complete this thesis. 

First of all, I am very greatful to Prof. Dr. Thomas Schultz for the support and guidance during the course this thesis. His insights have been very valuable for developing a consolidated research plan and viewing the research problem critically. He also made it possible for me to receive a fellowship from the DAAD (Deutscher Akademiker Austauchdienst). Without his nomination, I would not have received a fellowship position. I am also very thankful to him for delivering interesting and elucidate courses that sparked my research interests and propelled me to research on this topic.

Secondly, I would like to thank Mohammad Khatami for being my day-to-day supervisor and being very patient with all my questions. He gave me constant feedback and was immensely helpful solve implementational problems. 

I am also indebted to Dr. Regina Wehler whose Master Thesis Research made it easy for me to get started with my research topic.

Data were provided [in part] by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657)funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University. 
\vfill
\noindent%
\rule[1em]{8em}{0.5pt}  \hfill \rule[1em]{8em}{0.5pt}\\ % This prints a line to write the date
Location, Date \hfill Signature\\
